\documentclass[12pt,letterpaper,oneside]{book}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{cleveref}

\crefformat{chapter}{\S#2#1#3}
\crefformat{section}{\S#2#1#3} % see manual of cleveref, section 8.2.1
\crefformat{subsection}{\S#2#1#3}
\crefformat{subsubsection}{\S#2#1#3}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead[R,L]{}
\fancyhead[C]{\leftmark}

\makeatletter
\@addtoreset{chapter}{part}
\makeatother

\title{Bylaws and Regulations \\ of \\ WPI Lens and Lights}
\author{WPI Lens and Lights}
\date{\today}

\begin{document}

\maketitle

\tableofcontents
\newpage

\part{Bylaws}

\renewcommand{\chaptername}{Article}

\chapter{Name and Purpose}

\begin{enumerate}

\item The name of this organization will be "WPI Lens and Lights" and hereafter referred to as "Lens and Lights" or the "Club".
\item Lens and Lights seeks to educate and enthuse its membership about the specifics of lighting, sound, and projection services. This is demonstrated through the service of events on the WPI campus and, periodically, to outside organizations.


\end{enumerate}

\chapter{Members}

\section{Classes of Membership} \label{sec:classesofmembership}

\begin{enumerate}

\item \label{itm:wpicommunity} Any member of the WPI community, as defined by the University, is eligible for membership.
\item \label{itm:classesofmembership} There will be four classes of membership in the Club: Associate, Active, Away, Alumni. 
\subitem Associate Member: A member who is associated with the organization but does not meet the requirements of any other class of membership.
\subitem Active Member: A member who, having met all requirements provided in \cref{itm:activation} of this section, is approved by the Executive Board.
\subitem Away Member: Any member who is granted such status by the Executive Board as allowed by \cref{itm:awaystatus} of this section. Away members are exempt from requirements necessary to retain active status. At the member’s return to the University they will be automatically reclassified as Active.
\subitem Alumni Member: A member who was Active at the time of leaving the University, or who has been granted such status by the Executive Board as allowed by \cref{itm:deactivation} of this section. An Alumni Member may not be reclassified except as provided for in \cref{itm:expulsion} and \cref{itm:reactivation} of this section.
\item \label{itm:association} A member of the WPI community may become an Associate Member by demonstrating an interest in Lens and Lights.
\item \label{itm:activation} An Associate member may only be reclassified as an Active Member (“activated”) with the approval of the Executive Board. The Executive Board will consider any Associate member for activation at the first Executive Board meeting following fulfillment of the following requirements within a semester: (1) attends at least three business meetings and/or Executive Board meetings; (2) works at least five events including 1 each of lighting, sound, and projection. In extenuating circumstances, the Executive Board may waive said requirements.
\item \label{itm:deactivation} An Active member may be reclassified as an Associate member (“deactivated”) by the Executive Board. Any Active member who, in the immediate prior term (A,B,C or D), did not either work at least four events or attend at least one-half of the business meetings will be considered for deactivation by the Executive Board. In determining whether an Active member should be deactivated, the Executive Board will consider the reason for the member’s failure to meet the requirements and the interest in the Club they have demonstrated. Following a seconded motion to deactivate an Active member, the member will be notified of the motion. The motion may not be put to a vote until the next Executive Board meeting. Upon the request of the member, the Executive Board may elect to reclassify the member as an Alumni Member rather than an Associate Member.
\item \label{itm:expulsion} In matters where a member's actions have been determined to be detrimental to the Club, the Executive Board may revoke their membership in the Club.  The member in question may appeal the decision to the entire Club.
\item \label{itm:awaystatus} An Active Member who will be absent from the University for a period of off-campus academic activity may petition the Executive Board for Away status by submitting a written request which includes the period of time for which Away status is requested, the reason for it, and whether or not the member intends to retain voting privileges. 
\item \label{itm:alumnistatus} Any Active Member who leaves the University, by graduation or any other means, shall automatically be reclassified as an Alumni Member.
\item \label{itm:reactivation} An Alumni member, who is an Active member of the WPI community as defined by the University, may petition the Executive Board for reclassification as an Active Member. The Executive Board will consider such a petition with the same requirements for activation as those set in \cref{itm:activation} of this section.
\item \label{itm:associategraduation} An Associate member who leaves the University through graduation or other means will be removed from membership in the Club entirely.

\end{enumerate}

\section{Privileges of Membership}

\begin{enumerate}

\item Associate, Active, Away, and Alumni members may be members of crew for events, are entitled to notification of all meetings, and may participate in discussions at meetings.
\item At the discretion of the Executive Board, Active, Away, and Alumni members may be Crew Chiefs for events.
\item Active members and Away members retaining voting privileges may vote on all issues before the Club. These members will be considered the “voting membership”.

\end{enumerate}

\section{Duties of Membership}

\begin{enumerate}

    \item \label{itm:dutiesofmembership} When participating in any activity related to Lens and Lights, all members have a duty to comply with these Bylaws and with all written regulations approved by the Executive Board or the Club.
    
\end{enumerate}

\chapter{Officers}

The officers of the Club will be the President, Vice President, Technical
Director, Head Projectionist, Treasurer, Secretary, and Webmaster. The Executive Board is comprised of these officers and the Advisor.

\section{Duties of Officers}

\begin{enumerate}

\item The President is the primary representative of the Club and is responsible for smooth overall operation of the Club.
\item The Vice President assists the President with duties as assigned and
    serves as the liaison between the Club and any person(s) and/or organization(s) sponsoring an event. The Vice President is responsible for receiving and processing all work orders and for the organization and operation of work parties.
\item The Technical Director is responsible for all safety and training needed for safe and proper use of all equipment. The Technical Director will purchase new equipment per the direction of the club, perform maintenance and repairs to ensure proper equipment operation, and act as a technical liaison between the Club and other organizations.  The Technical Director will defer to the Head Projectionist on all matters related to the Booth.
\item The Head Projectionist is responsible for all projection related matters, including but not limited to overseeing all training in the use of projection equipment, maintenance of projectors, maintenance of the Booth, smooth operation of all projection events, and purchase of new equipment for the Booth per the direction of the club. The Head Projectionist will act in accordance with all applicable laws and regulations.
\item The Treasurer is responsible for all monetary matters of the Club, including but not limited to money transfers to and from the Club’s account, keeping a record of all such transactions, and billing and obtaining payment for services provided by the Club. Money may not be taken from or spent on behalf of the Club without prior approval from the Treasurer.
\item The Secretary is responsible for notifying members of all meetings, recording the minutes of said meetings, maintaining a system for storing documents pertaining to the Club and its operation, keeping and making available to all members a copy of these Bylaws, keeping records of the status of each member in the Club, maintaining mailing lists, and bringing forth activations and deactivations to the Executive Board. Upon becoming aware that an Associate member has met the activation requirements described in \cref{sec:classesofmembership} \cref{itm:activation}, or that an Active member has met the deactivation criteria described in \cref{sec:classesofmembership} \cref{itm:deactivation}, the Secretary must move to activate or deactivate such member, respectively, during the next or present Executive Board meeting.
\item The Webmaster is responsible for the operation of the Club’s online services. This includes the public-facing website, the internal database, and all Club social media and communication platforms. Additionally, the Webmaster works with the Technical Director to maintain any computers or mobile devices that the Club owns.
\item These officers shall, and have the authority to, fulfill all duties of their offices within the limits of these Bylaws.

\end{enumerate}

\section{Removal from Office}

\begin{enumerate}

\item An officer may resign from their position.
\item A two-thirds vote of the voting membership may remove any officer who fails to carry out the duties of their office.

\end{enumerate}

\section{Duties of the Executive Board}

\begin{enumerate}

\item The Executive Board will supervise the affairs of the club.
\item The Executive Board is subject to the orders of the Club. All actions taken by the Executive Board should be for the good of the Club and must not go against any action taken by the Club.
\item The Executive Board will ensure that business meetings and Executive Board meetings are held at least once a month during A, B, C, and D terms in accordance with \cref{chap:meetings}.
\end{enumerate}

\chapter{Elections}

\section{Eligibility for Office} \label{sec:eligibilityforoffice}

\begin{enumerate}

\item All officers must be Active Members as defined in \cref{sec:classesofmembership} \cref{itm:classesofmembership}.
\item Any Active Member who is expected to be a full-time undergraduate student for the duration of the term of office is eligible for election to office.
\item No person will hold more than one office except as given in \cref{sec:summerofficer}.

\end{enumerate}

\section{Election of Officers} \label{sec:electionprocedures}

\begin{enumerate}

\item Nominations will be held annually at the second business meeting of C term. Elections will be held at the next consecutive business meeting. Notice of these meetings will be given at least seven days in advance of each meeting. Nomination and election procedures will be sent out with notification of both meetings.
\item Any eligible member, as defined in \cref{sec:eligibilityforoffice}, may be nominated to any office. All nominations must be seconded by another member. The nominee will then be given a chance to accept or decline their nomination. In order to run for a position, a candidate must have accepted their nomination prior to the start of voting. Absentee nominations, in the form of a written list of names, will be accepted by the President any time between the notice of nominations and the end of the nomination meeting.
\item At the meeting prior to nominations (the first business meeting of C term)  a motion can be brought forward to split the election into two meetings.
\item At the first election meeting, before any candidate has begun speaking, the quorum may vote to reopen nominations.
\item Officers will be elected in the following order: President, Vice
    President, Technical Director, Head Projectionist, Treasurer, Secretary, Webmaster.
\item Voting will be done by secret ballot. Each ballot should be in the form of the name of a candidate or the word abstain; any other text will count as a vote of no confidence.
\item \label{itm:votecounters} Votes will be counted by the tellers, who are either the Club’s Advisor, the Advisor’s designees, or two alumni members appointed by the Executive Board.
\item Absentee ballots will be accepted in the form of written communication
    containing an ordered list of names, abstain, or no confidence in descending
    preference, for each office. This written communication should be submitted
    to the person(s) counting votes in accordance with \cref{itm:votecounters}
    of this section. Absentee ballots for a given office must be received prior
    to the start of vote counting for that position. Absentee ballots will only
    be counted if the member submitting them is not currently present at the
    meeting. Absentee ballots shall not count towards quorum. \item The first
    nominee to get greater than 50 percent of non-abstaining votes cast for an
    office will be elected to that office.
\item  In the event that no nominee for a particular office receives greater than 50 percent of votes cast, a runoff election shall be held by eliminating the nominee receiving the least votes. If two or more nominees are tied for least votes, discussion shall resume and a re-vote shall be held with identical candidates. This procedure shall continue until one nominee receives a simple majority. If “no confidence” receives said majority, voting for that office is closed and a special election is held at the next consecutive business meeting in accordance with \cref{sec:specialelections}. A re-vote with identical candidates can only be held a maximum of twice per office before voting shall be closed and a special election for the office in question shall be held at the next consecutive business meeting in accordance with \cref{sec:specialelections}.
\item Tellers will present the results of the elections to the club before the election for the next position starts. Tellers will present the winner of the election but not present the number of votes for each candidate. 
\item The officers-elect shall assume office at the second Executive Board meeting following the conclusion of the elections.
\end{enumerate}

\section{Interim Officer}

\begin{enumerate}

\item If any officer is granted Away status, their office shall be vacated until their return and a special election shall be held to elect an interim officer. In the event that another officer is elected to the interim position, that officer’s office shall be vacated and there shall be a special election at the following business meeting for another interim officer. When the officer on Away status returns to Active status, all affected shall regain the positions to which they are duly entitled.

\end{enumerate}

\section{Summer Officer} \label{sec:summerofficer}

\begin{enumerate}

\item If any officer chooses to not fulfill their duties during the period from the last day of D term through the first day of A term, or for a smaller period thereof, an interim officer shall be nominated by the current officer and brought before the Executive Board for approval. Once approved, the interim officer shall be conferred all the rights, privileges, and duties of a full-term Executive Board member for the agreed upon period.
\item During this period, a member may hold more than one office provided that no single member hold the majority of the offices, and that no single member simultaneously holds the offices of Technical Director and Treasurer.

\end{enumerate}

\section{Special Elections} \label{sec:specialelections}

\begin{enumerate}

\item In the event that any office becomes vacant, a special election shall be held at the next business meeting to fill the office. Special elections follow the same procedures as given in \cref{sec:electionprocedures}, except as provided in this Section.
\item Nominations and elections shall be held at the same meeting.
\item  Before nominations close, the teller(s) will cast a nomination for any member listed on an absentee ballot who has not yet been nominated. The teller(s) will also second a nomination made by a present member if the nominated member is listed on an absentee ballot.
\item Notice of special elections must be given at least 48 hours in advance of the election. A description of special elections shall be sent out with this notice.

\end{enumerate}

\chapter{Advisor}

\begin{enumerate}

\item The Advisor will be selected by the Executive Board with the aid of the University and shall be approved by a two-thirds majority vote of the voting membership.
\item The Advisor will not have voting privileges in any matters.
\item The Advisor will act as a consultant in all matters before the Club.
\item The Advisor will attend meetings and activities of the Club as seen fit and is entitled to all notifications given to members.

\end{enumerate}

\chapter{Meetings} \label{chap:meetings}

\begin{enumerate}

\item Regular business meetings of the Club will be held at least once per month during A, B, C, and D terms. Additional meetings may be called by the Executive Board or upon the request of one-third of the Active Members.
\item All business meetings are open to all.
\item A quorum will exist for a business meeting if more than half of the voting
    membership of the Club is present in person or via online meeting. Voting
    members of the Club who submit an absentee ballot will be counted towards
    quorum, except for the election of Officers.
\item A quorum is required for a vote to be taken.
\item Executive Board meetings will be held at least once a month during A, B, C, and D terms. Meetings may be called by the President, the Advisor, or two members of the Executive Board.
\item \label{itm:closedmeetings} All Executive Board meetings will consist of a portion open to all members of the club followed by a closed portion. Meeting minutes of the closed portion will be kept separately.
\item A quorum will exist for an Executive Board meeting if more than half of the Officers are present.
\item Active members and Away member retaining voting privileges must be notified of all business and Executive Board meetings at least 24 hours prior to the meeting.

\end{enumerate}

\chapter{Committees}

\begin{enumerate}

\item Committees will be appointed by the President or the Executive Board when such committees are deemed necessary to carry out the work of the Club.
\item The President is considered an ex-officio member of all committees.

\end{enumerate}

\chapter{Appointed Positions}

\begin{enumerate}

\item \label{itm:execboardappoints} The Executive Board reserves the right to create and dissolve Appointed Positions, and to appoint and remove members from these positions as they see fit.
\item All members appointed to such positions must be Active Members.
\item The provisions of \cref{itm:execboardappoints} of this section notwithstanding, the positions of Facilities Liaison and Repeater Manager must exist and be filled consistently.
\subitem Facilities Liaison: The Facilities Liaison will act as a liaison between the Club and Facilities in any way deemed necessary for the good of the Club. The Facilities Liaison is appointed jointly by the Executive Board and the Department of Facilities and is expected to be a three and a half year position.
\subitem Repeater Manager: The Repeater Manager will be in charge of managing the Club’s repeaters, loaner radios, and all associated paperwork.
\item \label{itm:appointeddates} When appointing a replacement member to fill an Appointed Position vacancy, the Executive Board will specify a date on which the newly-appointed member will assume the position. It is the responsibility of the incoming and outgoing holders of the specified Appointed Position to ensure a smooth transition of responsibilities on or before the date specified.

\end{enumerate}

\chapter{Parliamentary Authority} \label{chap:parliamentaryauthority}

\begin{enumerate}

\item The rules contained in the current edition of \textit{Robert's Rules of Order Newly Revised} govern this organization in all cases to which they are applicable and in which they are not inconsistent with these Bylaws.
\item \label{itm:bylawssupersede} In the event that a conflict exists, these Bylaws will supersede any appendix of these Bylaws and any other club document.

\end{enumerate}

\chapter{Amendments}

\begin{enumerate}

\item Any voting member may propose amendments to these Bylaws, or appendices thereof, in writing to the Executive Board. The Executive Board must present all proposed amendments to the Club within the next two business meetings.

\item A vote to amend these Bylaws will be taken at the next consecutive business meeting after such changes have been presented to the club.

\subitem A two-thirds majority of the voting membership will be required to pass any amendment. Voting will take place by a show of hands for and against the proposed amendment unless a voting member requests a vote by secret ballot.

\subitem In the event of a vote by secret ballot, votes will be counted by either the Club’s Advisor, the Advisor’s designees, or two alumni members appointed by the Executive Board.

\subitem Absentee ballots are permitted and must be received prior to the start of voting for a given amendment. Absentee ballots will only be counted if the member submitting them is not present at the business meeting. Absentee ballots shall remain valid if a friendly amendment to the given bylaw amendment is accepted by greater than 50 percent of the voting members present.

\subitem Multiple amendments may be voted on together unless a motion is made and seconded to vote on a particular amendment individually. 

\item A vote to amend an appendix of these Bylaws will be taken at the next consecutive business meeting after such changes have been presented to the club.

\subitem A simple majority of the voting membership will be required to pass the amendment. Voting will take place by a show of hands.

\subitem Absentee voting will be permitted. Absentee votes must be submitted to the President no later than the beginning of the voting meeting. Absentee votes will only be counted if the member submitting them is not present in the room.

\item At least once every two years, the Executive Board will appoint a committee to review the current Bylaws and, if necessary, propose amendments to such Bylaws to the voting membership.

\end{enumerate}

\chapter{Emergency Powers Clause}

\begin{enumerate}

\item In certain circumstances, it may become necessary for these Bylaws to be suspended or modified in part or in full.
\item The decision to suspend or modify all or part of these Bylaws rests solely with the Advisor of the Club. Any action taken by the Advisor shall be informed by discussion with the Club's Executive Board.
\item When the Bylaws are suspended or modified an expiry date for the changes will be set forth by the Advisor. 
\item Should these Bylaws be suspended or modified, a formal written notification to the membership will be made at the earliest possible convenience following the Advisor's decision.
\item The suspensions or modifications of these Bylaws may be reversed by a two-thirds vote of the voting membership.

\end{enumerate}

\chapter{SOC Enabling Clause}

WPI Lens and Lights agrees to abide by the policies of Worcester Polytechnic Institute as well as all federal, state, and local laws. Any changes to these Bylaws shall follow, in word and spirit, all University policies and all federal, state, and local laws.

\part{Regulations}

\renewcommand{\chaptername}{Chapter}

\chapter{Preamble}

These regulations are adopted by the Executive Board or the Club to supplement the Bylaws. Per \cref{chap:parliamentaryauthority} \cref{itm:bylawssupersede} of the Bylaws, the bylaws supersede these regulations in the event of a conflict. All members have a duty to comply with these regulations when working for Lens and Lights or otherwise participating in any activity related to Lens and Lights. Violation of these policies may be cause for disciplinary action by the Executive Board. As noted within, some of these regulations are only relevant to certain Officers' functions whereas others pertain to all members.

\chapter{Code of Conduct and Procedure}

\section{Key Regulations}

\begin{enumerate}

\item An officer will keep their keys on their person or in the lockbox in the office.
\item The club members can contact the President to request a temporary ID, which may be picked up and returned to campus police, when a need exists. They may request to borrow keys from an officer when a need exists.
\item It is the responsibility of the crew chief to see that they have keys prior to the setup of an event and to secure them for the duration of the event.
\item The keys must be returned to the officer from whom they were obtained as soon as possible.
\item The person who obtains the keys from an officer will be responsible for their use until they are returned to that officer.
\item Key use must obey all policies set forward by WPI, including that keys may not be taken more than 1 mile from campus. If an officer is leaving campus, they must secure their keys in the lockbox.
\item Misuse of the keys or negligence by a member may be cause for the Executive Board to take disciplinary action.
\item If an officer is involved with an organization that is actively renting items from Lens and Lights, said officer must lock their officer key ring in the lock box for the duration of the rental period.

\end{enumerate}

\section{Membership}

\begin{enumerate}

\item A member's status change from active to associate will not be effective until they are contacted by an officer.
\item A member whose status has been changed has the right to appeal this decision to the Executive Board.
\item A member whose status has been changed from associate to active shall be
    informed of this change at the general body meeting following their
    activation and not before. However, the Secretary or their designee may
    inform the member of the date of their activation after the Executive Board
    approves the reclassification.
\item A member can request away status for a specific period of time by emailing the Executive Board.  An active member can request to keep their voting rights while on away status.

\end{enumerate}

\section{Training}

\begin{enumerate}

\item The Technical Director and Executive Board will be responsible for establishing a training program for those members who desire to be trained.
\item Crew chiefs are expected to have a thorough knowledge of the equipment being used. If they are unsure of how to use equipment, they are expected to reach out to a knowledgeable member or the Technical Director before the event.
\item The Head Projectionist is responsible for training all Projectionists In Training (PITs).
Passed Practical Projectionists may assist in the training of PITs, given the prior permission of the Head Projectionist.
\item Any rigging related activities including truss, chain motors, battens and fly track systems, may only be performed by members who have received all required training. The Technical Director or their designee is responsible for all rigging related training.
\item Any lifts, including the Genie mast lift, Skyjack 3219, Skyjack 3226, and Genie boom lift, may only be operated by members who have received official lift training within the past 3 (three) years. Lift training shall be coordinated by the Technical Director and/or Facilities Liaison with WPI Environmental Health \& Safety. The Technical Director may revoke a member's permission to use lifts due to unsafe operation.
\item The Skyjack 3226 and Genie boom lift may only be operated by the Technical Director, Facilities Liaison, or their designee upon permission from WPI Environmental Health \& Safety. Lifts may only be operated outdoors or moved between buildings by the Technical Director, Facilities Liaison, or their designee.

\end{enumerate}

\section{Financial Policy}

\begin{enumerate}

\item No person may use the Lens and Lights Club equipment for personal monetary gain.
\item Any funds received by the Club or by the Club's members for services rendered will be forwarded to the Club's account.
\item The Executive Board will determine a price list for organizations requesting Club services.
\item The Executive Board will put to Club vote any expenditure over \$250 except for expendables and equipment repairs.
\item Any expenditure not voted on by the Club must be approved by the Executive Board.
\item The Technical Director and the Head Projectionist may purchase individual items costing less than \$50 each with the approval of only the Treasurer.
\item A meeting will be held annually to select new equipment to purchase during the following fiscal year. Prior to this meeting, the Treasurer will make a recommendation for a budget for the new equipment. The new equipment recommended by this assembly will be voted on at a regularly scheduled general body meeting.
\item The Vice President must approve any rental of equipment. The Vice President will set rates for such rentals.

\end{enumerate}

\section{Borrowing Equipment}

Active members may borrow equipment under the following conditions:

\begin{enumerate}

\item Equipment may be borrowed for personal use. The borrowing of equipment for non-personal use may not be used as a substitute for services routinely provided by LNL.
\item The Executive Board reserves the right to reject unreasonable requests.
\item The approval of the Vice-President or the Executive Board is required to borrow equipment.
\item The member borrowing the equipment is fully responsible for the equipment in case of damage or loss.
\item The equipment may not be borrowed if it is required by the Club.
\item At the time that the equipment is borrowed, the Executive Board will be accurately informed of all equipment borrowed.
\item The equipment will be returned as soon as possible after its use.
\item No equipment may be borrowed for a period to exceed one week unless approved by the Executive Board.

\end{enumerate}

\section{Work Parties (Events)}

\begin{enumerate}

\item Under normal circumstances, Crew Chiefs should be assigned to an event during a business meeting between one and two weeks before the event. Crew Chiefs should only be assigned outside of a business meeting when the event was advertised in a business meeting and nobody volunteered or in exceptional circumstances.
\item When assigning Crew Chiefs for events, Active Members who are not Officers will have priority over Officers. Active Members, including Officers, will have priority over Away Members and Alumni Members.
\item The crew chief is responsible for the work party, the equipment being used, the safety of all parties, and the professional completion of the task.
\item An officer will not interfere with a crew chief's operation at an event
    unless the crew chief is not fulfilling their responsibilities.
\item The crew chief is responsible for the completion of the Crew Chief Report and the accurate listing of hours worked by each member of the crew.
\item Unauthorized personnel will be kept away from Club equipment. Non-members may not operate Club equipment unless necessary for a professional performance and until the parties accept responsibility for equipment used.
\item After an event, all equipment shall be returned as soon as possible to its proper place unless there is a reason to store it elsewhere.
\item Equipment that needs to be left unattended must be in a secure location. 

\end{enumerate}

\section{Rentals}

\begin{enumerate}

\item Lens and Lights is not a rental house. Events have always been and will remain first priority for the club. The decision to rent equipment rests solely with the LNL Executive Board, and rentals will only be approved when the Executive Board can be assured that the equipment will be used by trained personnel.
\item Events are given priority over rentals. Equipment that is required for an event is not available to rent.
\item When equipment is rented, the renter will be required to sign a contract agreeing to pay for the repair or replacement of any damaged or lost equipment.
\item The Vice President or their designee must give approval for additional items to be rented following the original rental load out. Under no condition may items be taken without prior approval being granted. Any item taken without permission may be recalled at the discretion of the Executive Board.

\end{enumerate}

\section{General Operating Procedure}

\begin{enumerate}

\item A movie may be previewed only if approved by the Head Projectionist. In situations where the license to show the film is held by an outside organization, permission must be obtained from that organization prior to the showing. Previews are open only to Club members and guests approved prior to the preview by the Head Projectionist.
\item Only projectionists who have passed a practical and Projectionists-in-Training are permitted to use the 16/35/70mm and digital projectors with permission from the Head Projectionist.
\item In the Perreault Hall booth, the crew chief may limit the number of people in the booth and who they may be.
\item Unauthorized access or unauthorized presence in any of Lens and Lights' facilities is strictly prohibited and may result in disciplinary action by the Executive Board.
\item No fooling around or smoking in the booths, closets or near the equipment.
\item Intoxication will not be tolerated as part of a work party.
\item All members attending a Club movie are expected to work as needed.
\item Only active members may bring guests to Club sponsored events, and only with prior officer approval.
\item No work should be done on non-projection related equipment without the Technical Director's permission except when the Technical Director is unavailable and the repair is necessary to complete work at an event. No work should be done on projection related equipment without the Head Projectionist's permission except when the Head Projectionist is unavailable and the repair is necessary to complete work at an event.
\item All work on Club equipment is to be documented in a manner such that it will be available to the entire Executive Board.
\item Misrepresentation of the Lens and Lights Club by a member may result in disciplinary action by the Executive Board.
\item The Technical Director shall inspect the Alden hang points each term.

\end{enumerate}

\chapter{Radio Usage Policy}

The Federal Communications Commission establishes rules and regulations for operation of licensed repeater systems. Whereas WPI Lens and Lights is one such licensee, the club has established the following rules and regulations for operation of radios under the club's license:

\begin{enumerate}

\item All users shall follow the regulations prescribed in FCC ``part 90" at all times.
\item No one shall use a personally owned radio under LNL's license without being duly authorized by the Executive Board.
\item The Executive Board shall accept applications for authorization to transmit from any Associate, Active, or Alumni members. Approval of such applications shall be at the discretion of the Executive Board.
\item Non-LNL members shall be permitted use of the repeater through established MOU's; temporary authorization to use a loaner radio may be granted by crew chiefs on a ``per event" basis provided the temporary user agrees to abide by all rules and regulations.
\item Radios used shall be type accepted for the Land Mobile Radio Service.
\item Radios used shall transmit an MDC-1200 ID code, as assigned by the Executive Board. Radios shall be programmed for pre-transmit ID with 500 milliseconds of pretime.
\item Traffic related to the LNL events and day to day operations shall take priority; traffic not related to LNL operations shall be kept to a minimum.
\item During an event, any crew chief of such event shall have the authority to request anyone cease transmitting should such transmissions be interfering with the performance of the event.
\item The Executive Board shall have final authority for enforcing all rules and regulations, including suspension or termination of privileges.
\item Complaints and correspondence regarding the radio system shall be submitted to the Repeater Manager, as appointed by the Executive Board.
\item Communications on the radio system shall at all times be professional in nature and free from obscene language.

\end{enumerate}

\chapter{W1LNL Callsign Usage Policy}
Lens and Lights owns an amateur radio callsign, W1LNL. Use of this callsign is
restricted to Active and Alumni members, with permission from the Repeater
Manager or the Executive Board.

The W1LNL callsign may only be used for the following uses:
\begin{itemize}
\item Contests
\item Awards
\item Special Events
\item DX
\item Additional events or usages at the discretion of the Repeater Manager or
    the Executive Board
\end{itemize}

Note that the W1LNL callsign may not be used for general chat.

The W1LNL callsign does not confer any additional privileges beyond any member's
amateur license. Members may not use the W1LNL callsign to operate outside of
their license privileges. Use of the W1LNL callsign is subject to the approval
of the Repeater Manager and/or the Executive board. Members wishing to make use
of the callsign should contact the Repeater Manager in advance of their planned
usage. Authorization can be revoked at any time by the Repeater Manager or the
Executive Board.


\chapter{Card Access Policy}

\section{Purpose}
The purpose of this chapter is to outline the different card access levels with regards to Lens and Lights (LNL) and to define a policy for managing these access levels.

\section{Card Access Levels}
There are three (3) access levels in the card access system for Lens and Lights. They are, as the names appear in the card access management system for WPI:

\begin{itemize}
    \item Student Org - Lens n Lights - Current Executive Board
    \item Student Org - Lens n Lights - Event Card (Loaner)
    \item Student Org - Lens n Lights - Office Group
\end{itemize}

These access levels each serve a different purpose as described in the following subsections. They are herein referred to without the preceding ``Student Org - Lens n Lights - ''.

\subsection{Current Executive Board}
The Current Executive Board access level, sometimes colloquially referred to as "online" card access, provides access to many places around campus where LNL operates including but not limited to Alden Hall, Harrington Auditorium, and the Campus Center.

\subsection{Event Card (Loaner)}
The Event Card (Loaner) access level provides the same access as the Current Executive Board access level. While functionally the same, it is important to separate the loaner cards into a different group to ensure when making changes to other groups the loaner cards are not unintentionally affected.

\subsection{Office Group}
This access level provides access to the LNL Office in the Campus Center.

\section{Access Level Management}
This section outlines how the card access levels are managed including who gets each access level and for how long they get that access.

\subsection{Current Executive Board}
This access level is given to current members of the Executive Board, as well as Interim Officers, the Club Advisor, and the Facilities Liaison.

\subsubsection{Officers Elected in C-term}
All officers elected during the C-term elections shall be given this access level for the duration of their term. The expiration date shall be set to one month after the following year's election.

\subsubsection{Interim Officers}
When an interim (or summer) officer takes office, they shall be granted this access level. The expiration date shall be set to one week after the original executive board member retakes their position. The original Executive Board member shall not be removed from Current Executive Board during their leave of absence.

\subsubsection{Facilities Liaison}
To fulfill the duties of their job, the Facilities Liaison regularly requires access to many places around campus where LNL operates. As such, they shall be given the access level of Current Executive Board once the Executive Board confirms their position. The expiration set shall be set to May 31st of their expected graduation year to allow transition time for the incoming Facilities Liaison.

\subsubsection{Advisor}
The advisor of the club shall be given this access level. The expiration date shall not be defined.

\subsection{Event Card (Loaner)}
This access level shall only ever contain the LNL Temporary IDs. Their expiration shall not be defined.

\subsubsection{Lost Temp ID}
In the event an LNL Temporary ID is lost it will be immediately reported to campuscardaccess@wpi.edu as lost to be marked as such in the card access system and deactivated. If found again, the same process may be used to request it be reactivated in the system.

\subsection{Office Group}
This access level shall be given to former members of the Executive Board, the Repeater Manager, and any Passed Practical Projectionists as given below.

\subsubsection{Former Executive Board Members}
Any individual who has, at any point, sat on the Executive Board of LNL shall receive this access level. To ensure continuous access, individuals shall be given this access level upon taking office with no expiration date defined.

\subsubsection{Repeater Manager}
The Repeater Manager, as appointed by the Executive Board, shall receive this access level with an expiration date set to May 31st of their expected graduation year. If at any point the Repeater Manager steps down from their position, unless they are entitled to this access level per other means they shall have this access level revoked.

\subsubsection{Passed Practical Projectionists}
Any projectionist who successfully completes a ``practical'' to the satisfaction of the current Head Projectionist shall receive this access level. The expiration date shall not be defined.

\subsection{Discretion of Executive Board}
\begin{enumerate}
    \item Card access is a privilege granted to members of the club. The
        Executive Board can revoke any card access within its purview.
        Should a member be found to be misusing their
        access, the Executive Board shall review their access accordingly.
    \item The President shall be responsible for working with relevant campus
        departments to maintain card access and communicating changes in a timely manner
    \item The Facilities Liaison can assist the President with card access
        management and communications.
\end{enumerate}
\end{document}
