\chapter{Cancellation Policy}

\section{Introduction} 
Lens and Lights wants to put on the best event possible for all clients. However,
there are often times where external conditions force the cancellation of an
event. This policy documents the conditions of cancellation, and any additional
terms or fees that may apply.

\section{Cancellation by the Client}
\begin{enumerate}
    \item Any Client may cancel their event by submitting a written request to
        Lens and Lights.
    \item Cancellation requests received prior to the start of setup for an
        event will incur no cost, outside of external rental or movie right
        fees.
    \item Once setup for an event has started, service fees will still apply,
        subject to discounts at the discretion of Lens and Lights.
    \item Once an event has begun, the full cost of Lens and Lights services
        will apply.
\end{enumerate}

\section{Cancellation by Lens and Lights}
\begin{enumerate}
    \item If the scope of an event changes, Lens and Lights may not be able to
        adapt its setup, and may not be able to provide services.
    \item At Lens and Lights' sole discretion, it may cancel events if they
        would present an undue hardship on its crew.
    \item Lens and Lights will make every effort to make this determination
        prior to the start of setup for an event.
    \item Lens and Lights may elect to cancel an event during the event or setup
        if the Client or event participants do not treat crew members
        respectfully or professionally.
\end{enumerate}
Lens and Lights will put on a good faith effort to make sure that every
confirmed
event happens. However, in some cases, such as if the scope of an event
increases drastically, LNL may elect to not provide services to the event. At
LNL’s sole discretion, it may cancel events if they would present an undue
hardship on its crew. LNL will make every effort to make this determination
prior to the start of setup for an event, in which case no fee will apply,
except for negotiated rental costs that cannot be cancelled.

Lens and Lights may also elect to cancel an event during the event or LNL setup
if the Client or event participants do not treat LNL members or Crew Chiefs with
respect.
