\chapter{General Event Policy}

\section{Introduction}
Lens and Lights provides services to hundreds of student and department events
each year. Part of that includes making sure that all events and clients are
adequately prepared.

\section{Definitions}
\begin{enumerate}
    \item \emph{Large Event Space} -- Alden Great Hall, Rec Center Courts, Quad,
        Harrington Auditorium
    \item \emph{Authorized Client Representative} -- Unless otherwise
        communicated, any member of a club executive board is an Authorized
        Representative, or a member of the Department.
    \item \emph{Confirmation} -- To have a confirmed event, an Authorized Client
        Representative must confirm in writing to the quote sent by the Lens and
        Lights.
\end{enumerate}

\section{Required Client Preparations}
\begin{enumerate}
    \item Clients are encouraged to reach out as early as possible to reserve
        services from Lens and Lights. Requests submitted with less than two
        weeks notice may incur late fees at the discretion of Lens and Lights.
    \item In order to confirm your event with Lens and Lights, Clients must
have a confirmed event space reservation through the WPI Events Office.

\item Clients are required to provide the following information prior to
    confirming their event:
    \begin{itemize}
        \item Location
        \item Date
        \item Time (Setup by, event start, event end)
        \item Inclement weather plan, if applicable
        \item Categories \& scope of services (Lighting, Sound, Projection)
        \item Billing information (Worktag, sponsoring organization)
    \end{itemize}

    Location, date, and times are only valid once confirmed by the WPI Events
    Office.

\item Clients are responsible for coordinating with the WPI Events Office,
    other service providers, and performers.
    \begin{itemize}
        \item If performers provide technical riders, Clients must provide said
            riders to Lens and Lights in a timely manner.
        \item Clients are responsible for any costs incurred in fulfilling
            technical requirements. Lens and Lights will keep Clients informed
            of charges incurred.
        \item Lens and Lights reserves the right to coordinate directly with
            performers.
    \end{itemize}

\item Clients are expected to keep Lens and Lights apprised of any changes in
    event scope, time, location, billing information, or other details. Late
    fees may be incurred if details change within two weeks of the event. Lens
    and Lights may not be able to fulfill requests made within two weeks.

\item All events are required to follow the Lens and Lights Inclement Weather
    Policy.
\end{enumerate}

\subsection{Inclement Weather Plans}

\begin{enumerate}
    \item All events taking place outdoors or in locations affected by weather
        are required to complete an Inclement Weather Plan.
    \item Inclement Weather Plans must include:
        \begin{itemize}
            \item Defined plan of action (cancellation, postponement, moving to
                a different location, scaled-down event, etc.).
            \item Alternative locations/times (if applicable)
            \item Day-of contact who is authorized to make weather calls (as
                defined in the Inclement Weather Policy).
            \item Latest time that a weather call will be made by the Client in
                advance of setup.
        \end{itemize}
    \item All alternate dates and/or locations must be reserved in advance with
        the WPI Events Office.
\end{enumerate}

\section{Setup Time}


Setup time is determined on a per-event basis by Lens and Lights, and may vary
significantly. Lens and Lights cannot confirm an event without adequate setup
time as determined by Lens and Lights.


{\Huge If Lens and Lights is unavailable during available setup times, Lens
and Lights may not be able to confirm the event.}

\subsection{Rules of Thumb}

\begin{enumerate}
    \item Event setups in Large Event Spaces require at least eight hours of
setup time. 
    \item All events require at least three hours of setup time.
    \item Lens and Lights prefers to set up on evenings and during weekends.
\end{enumerate}

\begin{enumerate}
    \item 
\end{enumerate}

Lens and Lights requires setup time to prepare for an event. The exact amount of
time varies depending on the scope of the event and existing equipment in the
space. In general, if there is already equipment in the air in a space, Lens and
Lights will require at least three hours of dedicated setup time. If there is
not already equipment set up in large spaces (including Alden Great Hall, Rec
Center Courts, and Harrington Auditorium), Lens and Lights will require at least
eight continuous hours of dedicated setup time. In extra-large spaces such as
Harrington Auditorium, Lens and Lights may require more than this time. This
setup time must be confirmed with the Events Office after consultation with Lens
and Lights.

\section{Rentals}

Some events may require additional equipment beyond the scope of Lens and
Light's equipment. Such events, at the discretion of Lens and Lights as well as
the agreement of the client, may negotiate equipment rentals with external
vendors. Such rentals will be billed to the client at cost, plus additional fees
at the discretion of Lens and Lights.

